|

### 2020-01-22 nontex/revealjs/_guide/fs_revealjs_basics.Rmd
mathjax basic

>>>>

In *serif_fan.css* To change main body font, change font-size below.

```
.reveal p {
  margin: 20px 0;
  font-size: 1em;
  line-height: 1.3; }
```

To change MathJax font size, add to end of *serif_fan.css*:

[MathJax, how to change text size?](https://stackoverflow.com/questions/48136559/mathjax-how-to-change-text-size)
[How to change font for MathJax](https://stackoverflow.com/questions/41474096/how-to-change-font-for-mathjax)

```
.math span {
  font-size: 12px;
}
```
